\documentclass[12pt]{article}
 \usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{tikz}
 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip\labelsep{\bfseries #1}\hskip\labelsep{\bfseries #2.}]}{\end{trivlist}}

 
\begin{document}
%\renewcommand{\qedsymbol}{\filledbox}
%Good resources for looking up how to do stuff:
%Binary operators: http://www.access2science.com/latex/Binary.html
%General help: http://en.wikibooks.org/wiki/LaTeX/Mathematics
%Or just google stuff
\title{Graph Theory: Homework 4}
\author{Bilal Abu Saad}
\maketitle
 
\begin{problem}{1}
Prove or disprove: If P is a $u$, $v$-path in a 2-connected graph G, then there
is a $u$, $v$-path Q that is internally disjoint from P.
\end{problem}
 
\begin{proof}
  The statement is false, consider the following graph:\\
  \\
  \\
  \\
  \\
\end{proof}

\begin{problem}{2}
  Given a simple connected graph G, obtain G$'$ by adding an edge joining every
  pair of vertices whose distance in G is 2. Prove that G$'$ is 2-connected.
\end{problem}

\begin{proof}
  To prove this we will show that for any two distinct vertices $u$ and $v$ in
  $G'$, there exists a cycle in $G'$ that contains them. We proved that this is
  equivilant to 2-connectedness in class.
  We will prove this using induction on the length of the shortest path between
  $u$ and $v$ in $G$. \\
	Base case:
	\begin{itemize}
		\item{$n=1$} \\
			Here we have that $(u, v) \in e(G)$, since $|v(G)| > 2$ and $G$ is
      connected $\exists w \in G$ s.t $w \neq v$,  $w \neq v$ and $w$ is
      connected to atleast one of $u$ or $v$. W.l.g assume $(u, w) \in e(G)$,
      therefore in $(v, w) \in G'$ (either it was in $G$ else the distance
      between $v$ and $w$ is 2 and the edge was added in $G'$).\\
      So we have a cycle $(u, v, w, u)$ in $G'$.
	\end{itemize}
	Hypothesis: We assume that the the cycle condition holds 
  $\forall_{u v \in v(G)}$ s.t $\delta(u,v) = k < n$ and prove for
  $n$ \\
	Step: \\
	Let $P$ as: $(u = v_1, \ldots, v_{n-2} ,v_{n-1},v_n = v)$, be a shortest path
  of length $n$ between $u$ and $v$.
  From the inductive hypothesis we know that there is a cycle in $G'$ such that
  both $u$ and $v_{n-2}$ are in it. We can extend this cycle with the following
  cycle $C_1 = (v_{n-2}, v_{n-1}, v, v_{n-2})$ which will also be a cycle that
  contains both $u$ and $v$. We need to show that $C_1$ exists in $G'$, the
  first two edges are a part of $P$ so they must be in $G$ and in $G'$, now the
  last edge: $(v, v_{n-2}) \in e(G')$.\\
  Claim: $(v_{n-2}, v_n)$ was
      added in the construction of $G'$. To show this, we need to prove that
      $\delta_{G}(v_{n-2}, v_n)= 2$. 
			\begin{itemize}
        \item $\delta_{G}(v_{n-2}, v_n) \le 2$ This is true because $(v_{n-2},
          v_{n-1}, v_{n})$ is a part of $P$.
				\item $\delta_{G}(v_{n-2}, v_n) \ge 2$ \\
        $\bullet$ This is true because $(v_{n-2}, v_{n-1}) \not\in e(G)$, this
          is because $P$ is
          a shortest path (I.e if this edge was in we could make P shorter by
          1).\\
				$\bullet$ $v_{n-2} \neq v_n$: $n > 1$
			\end{itemize} 
\end{proof}

\begin{problem}{3}
  Let $G$ be a connected graph in which for every edge $e$, there are cycles
  $C_1$ and $C_2$ containing $e$ whose only common edge is $e$. Prove that $G$ is
  3-edge-connected.
  Use this to show that the Petersen graph is 3-edge-connected.
\end{problem}

\begin{proof}
  Let $F = [S, \overline S]$ be a minimum edge cut of $G$ such that $G - F$ is
  disconnected. Let $uv = e \in F$. The vertices $u$ and $v$ must be in
  different sides of the edge cut. We know that $e$ is in two cycles $C_1$ and
  $C_2$ such that $C_1 \triangle C_2 = {e}$ since these cycles start from $S$
  and end in $\overline S$ they must have edges $e_1$ and $e_2$ respectively,
  that cross $[S, \overline S]$, obviously $e_1 \neq e$ and $e_2 \neq e$ since
  $C_1$ and $C_2$ are cycles. Hence $F$ has atleast three edges.
\end{proof}
\begin{proof}{Peterson thing}\\
  In handwriting.
\end{proof}

\begin{problem}{4}
  Let $G$ be an $r$-connected graph of even order having no $K_{1,r+1}$ as an
  induced subgraph, for some $r \ge 1$. Prove that $G$ has a $1$-factor
\end{problem}
\begin{proof}
  We will show that Tutte's condition holds for $G$. I.E. $\forall_S$ $S \subseteq
  V(G)$, $o(G - S) \le |S|$.\\
  Let $S \subseteq V(G)$, consider the following cases:
  \begin{itemize}
    \item{$S = \phi$}\\
      Since $G$ is connected and of even order $o(G-S) = 0$ so Tutte's condition
      holds for this case.
    \item{$ 1 \le |S| < r$}\\
      $G - S$ is connected, since we had even order, $o(G-S) \le 1$ depending on
      the size of $S$, but $S \ge 1$ hence Tutte's condition holds.
    \item{$|S| \ge r$}\\
      $G-S$ is disconnected, let $C_1 \ldots C_k$ denote the connected
      components of $G-S$.
      \begin{lemma} 
        $\forall i \in {1 \ldots k}$ $|[S, C_i]| \ge r$
      \end{lemma}
      There are atleast $kr$ edges coming into $S$ (from lemma 1), since $|S| <
      k$, from the pigeon hole principle, there will be an element of $S$ that
      is connected to atleast $r + 1$ vertices outside of $S$, contradiciton to
      the fact that $G$ has no induced $K_{1, r+1}$. So $|S| \ge k$, $o(G - S)
      \le k \le |S|$. Hence Tutte's condition holds.
      \begin{proof}[proof of lemma 1]
        Each component of $G - S$ must have at least $r$ edges to vertices of S,
        if not, we could remove those edges from $G$ and disconnect the graph.
        This means that we could disconnect the graph with less than $r$ vertices
        contradiction.
      \end{proof}
  \end{itemize}
  We showed that Tatte's condition holds in $G$, hence it must have a 1-factor.
\end{proof}
\end{document}
